Rank Recovery

### 2020-11-09 output_scripts/rank_recovery.Rmd
degree corrected sim model and corresponding sim example

model3_stan_fit <- model3$sample(data = data_list,
                                num_warmup = 500,
                                num_samples = 500,
                                chains = 4, 
                                parallel_chains = 4,
                                refresh = 100)

@@

stansims <- rstan::extract(stanfit)
## truth is .1, .2, .4, .7, .9
apply(stansims$f, 2, mean)
apply(stansims$f, 2, sd)
```

@@

table(1:5,isi_rank)
```

>>>>

model3_stan_fit <- model3$sample(data = data_list,
                                iter_warmup = 500,
                                iter_sampling = 500,
                                chains = 4, 
                                parallel_chains = 4,
                                refresh = 100)

@@

stansims <- rstan::extract(stanfit)
## truth is .1, .2, .4, .7, .9
apply(stansims$f, 2, mean)
apply(stansims$f, 2, sd)

# most important is the order
m3_rank <- order(apply(stansims$f, 2, mean))
#order(apply(stansims$f, 2, sd))
```

@@

isi_rank
true_rank <- c(1:5)

table(true_rank, m3_rank)
table(true_rank, isi_rank)
table(isi_rank, m3_rank)
```

## Simulated from degree corrected model

How does this ranking inference compare when we instead simulate
data from the proposed degree corrected model.

```{r sim dc mmhp, cache=TRUE}
gamma_var <- c(0.01, 0.02, 0.03, 0.06, 0.07)
zeta_var <- c(0.075, 0.02, 0.03, 0.05, 0.08 )
lambda_dc_matrix <- outer(gamma_var, zeta_var, "+")
# lambda_dc_matrix

object_dc_matrix <- object_matrix
object_dc_matrix$lambda0_matrix <- lambda_dc_matrix

sim_model3_data_dc <- 
  simulateLatentMMHP(lambda0_matrix = object_dc_matrix$lambda0_matrix,
                      lambda1_matrix = object_dc_matrix$lambda1_matrix,
                      alpha_matrix = object_dc_matrix$alpha_matrix,
                      beta_matrix = object_dc_matrix$beta_matrix,
                      q1_matrix = object_dc_matrix$q1_matrix,
                      q2_matrix = object_dc_matrix$q2_matrix,
                      horizon = 200)
clean_sim_data_dc <- cleanSimulationData(raw_data = sim_model3_data_dc, 
                                        cut_off = cut_off, 
                                      N = length(object_par$f_vec_1))

```{r fit dc mmhp, cache=TRUE}
model3_dc <- cmdstan_model(here("lib","sim_model3_dc.stan"))
data_list_dc <- list(max_Nm = max(clean_sim_data_dc$N_count),
                    N_til = length(clean_sim_data_dc$I_fit),
                    M=sum(clean_sim_data_dc$N_count>=cut_off),
                    N=length(object_par$f_vec_1),
                    I_fit = clean_sim_data_dc$I_fit,
                    J_fit = clean_sim_data_dc$J_fit,
                    T = tail(clean_sim_data_dc$day_hour,1),
                    Nm = as.vector(clean_sim_data_dc$N_count[
                      clean_sim_data_dc$N_count 
                                                          >= cut_off]),
                    event_matrix = clean_sim_data_dc$event_matrix,
                    interevent_time_matrix = clean_sim_data_dc$time_matrix,
                    max_interevent = clean_sim_data_dc$max_interevent)

model3_dc_stan_fit <- model3_dc$sample(data = data_list_dc,
                                seed = 123,
                                iter_warmup = 500,
                                iter_sampling = 500,
                                chains = 4, 
                                parallel_chains = 4,
                                refresh = 100)

stanfit_dc <- rstan::read_stan_csv(model3_dc_stan_fit$output_files())
stansims_dc <- rstan::extract(stanfit_dc)
## truth is .1, .2, .4, .7, .9
apply(stansims_dc$f, 2, mean)
apply(stansims_dc$f, 2, sd)

# most important is the order
m3_dc_rank <- order(apply(stansims_dc$f, 2, mean))
```

Then we can compare the I&SI model here also.

```{r i and si dc}
count_data_dc <- get_wl_matrix(df = cbind(clean_sim_data_dc$start, 
                                       clean_sim_data_dc$end))
isi_dc.out <- compete::isi98(m = count_data_dc, random = TRUE)
isi_rank_dc <- as.numeric(rev(isi_dc.out$best_order)) # ranked from lowest to highest

isi_rank_dc
true_rank <- c(1:5)

table(true_rank, m3_rank)
table(true_rank, isi_rank)
table(isi_rank, m3_rank)
```

So when we consider this degree corrected model we also
correctly recover the latent ranking order in this simulation.
